Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization

### 2017-01-30 02_methods/methods.tex
Improve figure

\begin{figure*}
  \centering
  \hspace*{\fill}
  \subfigure[]{\label{subfig:pathhist}\includegraphics[width=1\textwidth]{02_methods/figures/heatmaprep.pdf}} \hfill
  \hspace*{\fill}
  \\
  \hspace*{\fill}
  \subfigure[]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2_annotated.pdf}} \hfill
  \hspace*{\fill}
  \caption{\subref{subfig:pathhist} Illustration of the heatmap representation: all \ac*{pdf}s of the prostate gland are concatenated together to build an heatmap; \subref{subfig:pat1}-\subref{subfig:pat2} Illustration of inter-patient variations (i.e., $\Delta_i$, $\Delta_t$, and $\alpha_i$) \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
  \label{fig:heatmap}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \hspace*{\fill}
  \subfigure[]{\label{subfig:pathhist}\includegraphics[width=1\textwidth]{02_methods/figures/heatmaprep.pdf}} \hfill
  \hspace*{\fill}
  \\
  \hspace*{\fill}
  \subfigure[Start of enh.: 6\textsuperscript{th} serie;
  initial intensity: 117; wider st. dev.]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1.pdf}} \hfill
  \subfigure[Start of enh.: 4\textsuperscript{th} serie;
  initial intensity: 103; narrower std. dev.]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2.pdf}} \hfill
  \hspace*{\fill}
  \caption{\subref{subfig:pathhist} Illustration of the heatmap
    representation: all \ac*{pdf}s of the prostate gland are
    concatenated together to build an heatmap;
    \subref{subfig:pat1}-\subref{subfig:pat2} Heatmap of 2 patients
    revealing  the three types of inter-patient variations: intensity shift
    ($\Delta_i$), time shift ($\Delta_t$), and intensity scale
    ($\alpha_i$). The intensity shift is observed by checking the
    variation of the value of the initial intensity. The time shift
    is observed by a difference of the start of enhancement. Finally,
    the intensity scale variation is observed by the difference of
    dispersion of the intensities.}
  \label{fig:heatmap}
\end{figure*}
